---
output: BiocStyle::html_document
toc: FALSE
---
<style>
@import 'https://fonts.googleapis.com/css?family=Inconsolata|Roboto:400,700';
body {
  font-family: Roboto !important;
}
pre code {
 font-family: Inconsolata !important;
}
a {
  text-decoration: none !important;
  color: #0A0A0A !important;
}
a:hover {
  color: #dd3333 !important;
}
h1, h2, h3, h4, h5, h6 {
  color: #4466ee !important;
  font-weight: bold !important;
}
</style>


# ch-01

## simple loop

Matloff says to keep it simple, so prefer oddcount1 over oddcount2.

```{r}
oddcount1 <- function(x) {
  k <- 0
  for (n in x) {
    if (n %% 2 == 1) k <- k + 1
  }
  return(k)
}

oddcount2 <- function(x) {
  k <- 0
  for (i in 1:length(x)) {
    if (x[i] %% 2 == 1) k <- k + 1
  }
  return(k)
}
```

## vectorise

Could also get rid of the loop entirely.

```{r}
oddcount3 <- function(x) {
  sum(x %% 2 == 1)
}
```

## speed test

Speed test shows speed benefits from vectorising.

```{r}
library(microbenchmark)

x <- sample(1:200, 50)
mb <- microbenchmark(
  "simple" = oddcount1(x),
  "c--ish" = oddcount2(x),
  "vector" = oddcount3(x)
)

mb
```


```{r}
library(microbenchmark)

mb <- microbenchmark(
  "range" = x[1:(length(x)-1)],
  "minus" = x[-length(x)],
  times = 1000L
)

mb
```

